\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}
\usepackage{hyperref}

% Sender address and contact details
\address{123 Maple Street\\
  Cityville, ST 12345\\
  Email: \href{mailto:alex@example.com}{alex@example.com}\\
Phone: (555) 123-4567}

% Signature block
\signature{Alex Taylor}
\date{April 7, 2026}

\begin{document}

\begin{letter}{name}

  \opening{Dear Mr. Smith,}

\end{letter}

% Recipient address
\begin{letter}{
    Mr. Jordan Smith\\
    Acme Corporation\\
    456 Oak Avenue\\
  Townsville, ST 67890}

  \opening{Dear Mr. Smith,}

  I hope you are doing well. I am writing to follow up on our recent conversation regarding the upcoming partnership between Acme Corporation and Maple Consulting.

  This letter provides a brief summary of the main points we discussed:

  \begin{itemize}
    \item Project timeline and key milestones
    \item Scope of services and deliverables
    \item Communication plan and reporting expectations
  \end{itemize}

  We are excited about the opportunity to collaborate and believe that this partnership will produce excellent results for both organizations.

  If you have any questions or would like to schedule a follow-up meeting, please let me know. I look forward to your response.

  \closing{Sincerely,}

  \ps{P.S. I will also send a draft agreement for your review by the end of the week.}

  \encl{Brochure and project summary}

\end{letter}

\end{document}
